NEED A BETTER TITLE: A co-moving pair of bright stars \\ with very different metallicities and abundances

### 2017-04-13 paper/ms.tex
NL for insights on scattering

\author{
  Semyeong Oh\altaffilmark{\pu,\lead},
  APW, JMB, KH, DWH, DNS
}

@@

The abundance of HD 30 is peculiar on its own compared to other disk stars with
similar $[\elem{Fe}/\elem{H}]$.
For a star with $[\elem{Fe}/\elem{H}] \approx 0.2$, we generally expect
$[\elem{Na}/\elem{Fe}] > 0$ and $[\elem{Mn}/\elem{Fe}] > -0.1$
(\citealt{Battistini:2015aa,Bensby:2003aa}) making the abundances of HD 30 ever more unlikely.
We stress that none of the \tood{how many} binary pairs examined in \citealt{2016ApJS..225...32B}
show discrepancies in abundances between the stars at this level.
In fact, no strong trend is found in pair for most elements
except N and Y.
For Y, the trend for this pair is opposite of the others in Teff.
Specifically, no difference within pair is found for Mn.
(see figure X in that paper; purple is this pair)

@@

\begin{figure}[htpb]
  \centering
  \includegraphics[width=0.9\linewidth]{relabun_tc.pdf}
  \caption{Abundance of HD 240430 ($[\mathrm{Fe}/\mathrm{H}] = 0.20$)
    relative to HD 240429 ($[\mathrm{Fe}/\mathrm{H}] = 0.01$)
    as a function of condensation temperature of elements (\citealt{2003ApJ...591.1220L}).
  }
  \label{fig:relabun_tc}
\end{figure}

@@

@@

>>>>

\author{
  Semyeong Oh\altaffilmark{\pu,\lead},
  APW, JMB, KH, NL, DWH, DNS
}

@@

The abundance of HD 30 is peculiar on its own compared to other disk stars with
similar $[\elem{Fe}/\elem{H}]$.
For a star with $[\elem{Fe}/\elem{H}] \approx 0.2$, we generally expect
$[\elem{Na}/\elem{Fe}] > 0$ and $[\elem{Mn}/\elem{Fe}] > -0.1$
(\citealt{Battistini:2015aa,Bensby:2003aa}) making the abundances of HD 30 ever more unlikely.
We stress that none of the \todo{how many} binary pairs examined in \citealt{2016ApJS..225...32B}
show discrepancies in abundances between the stars at this level.
In fact, no strong trend is found in pair for most elements
except N and Y.
For Y, the trend for this pair is opposite of the others in Teff.
Specifically, no difference within pair is found for Mn.
(see figure X in that paper; purple is this pair)

@@

\begin{figure}[htpb]
  \centering
  \includegraphics[width=0.9\linewidth]{relabun_tc_XH.pdf}
  \caption{Abundance of HD 240430 ($[\mathrm{Fe}/\mathrm{H}] = 0.20$)
    relative to HD 240429 ($[\mathrm{Fe}/\mathrm{H}] = 0.01$)
    as a function of condensation temperature of elements (\citealt{2003ApJ...591.1220L}).
  }
  \label{fig:relabun_tc}
\end{figure}

@@

estimate: 10 earth mass

@@

Change in stellar abundance due to ingestion of planets has been considered
for similar bright star pairs HD XX/XX (Mack) and HD XX/XX(Mack).

% Concluding remakrs
